Through the eyes of the teacher

### 2021-06-21 02_paper/schrott/paper_1_supplement_with_presence.Rmd
SRI / Erhebungsprotokoll / Versuchsleitungsmanual

affiliation:
  - id            : "1"
    institution   : "Leipzig University"
  - id            : "2"
    institution   : "Max-Planck University for Evolutionary Anthropology"

authornote: |
  The Ethics Advisory Board of Leipzig University has dealt with the research project and has come to the conclusion that there are no objections to the implementation of this research project. The Ethics Advisory Board points out that the scientific and ethical responsibilty for the implementation of the project remains with the project director.

@@

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf #bookdown::word_document2
---

@@

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

@@

## Procedure/ Data collection

### Set up

For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig. The subjects were divided into groups of four, so the study was conducted on two different sessions. All participants were asked to hold a 10-minute lesson. The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.

@@

### Questionnaire data

After each mini-lesson, the subjects answered items on the teaching quality using a validated questionnaire ((@helmke2014unterrichtsdiagnostik)) and scales on the teacher's presence behavior. An external observer also completed the questionnaire. In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire.

### Behavioral data

The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab. Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles. One camera was installed to film the class from the side. Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back. Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.

### Eyetracking data

A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants. The head unit is a measuring device with different sensitive sensors. A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds. Infrared light illuminators support the eye tracking sensors which record the eye orientation. The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second. The scene camera has a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height). The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.

## Coding/ Data preparation/ Reliability

### Questionnaire Data

The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
The scales on the quality of teaching are a validated questionnaire (@helmke2014unterrichtsdiagnostik). Whereas the scales on the teacher's presence behavior were derived from the research literature (@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen) and were used in the pilot for the first time.

@@

The table provides an overview over the mean, the range and standard deviation of all scales.

@@

\newpage
The individual items of a scale are further represented in graphs.

@@

(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention

```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}

@@

```
\newpage
In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.

```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE}

@@

### Behavioral Data

The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (@kuckartz2019analyzing). The following coding scheme was developed:

- phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
- phase - lesson end,	state event: teacher finishes the lesson with a noise, talk, taking a position in class
- phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working material, organizing desks, opening windows, printing work results etc.)
- phase - single,	state event: any individual student activity on a given task (reading, writing, drawing etc.)
- phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
- phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
- phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
- phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board, OHP etc.
- phase - other, state event: not categorizable
- phase - break, state event: e.g. drinking, relaxation exercises
- phase - external interruption, state event: external interruptions (e.g. fire alarm, technical problems, other teachers coming into the room)

- speaking time - teacher, state event
- speaking time - students, state event

- disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)

First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher. The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.

```{r coded speaking time, echo = FALSE}
### read in data for 01_01_expert_D
speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.01 <- speaking.data.01.01  %>% select(
  Dokumentgruppe,
  Dokumentname,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher and "kodiert von Anna" as row 
speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
                                           Dokumentgruppe == "kodiert von Anna")
speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)

# read in data for 01_02_expert_A
speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.02 <- speaking.data.01.02 %>% select(
  Dokumentname,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)

# read in data for 01_03_novice_B
speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.03 <- speaking.data.01.03 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)

# read in data for 01_04_novice_C
speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.04 <- speaking.data.01.04 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")

speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)

# read in data for 02_01_novice_A
speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.02.01 <- speaking.data.02.01 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)

# read in data for 02_02_novice_B
speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.02.02 <- speaking.data.02.02 %>% select(
  Dokumentgruppe,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
                                                       Dokumentgruppe == "kodiert von Anna")
speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)

# read in data for 02_03_novice_C
speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.02.03 <- speaking.data.02.03 %>% select(
  Dokumentgruppe,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
                                                       Dokumentgruppe == "02_03_kodiert von Anna")
speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)

# read in data for 02_04_novice_D
speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.02.04 <- speaking.data.02.04 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)

```{r speaking plot, echo=FALSE}

# read in table with coded speaking time included
speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)

# to compare both sessions filter only Identical items
speaking.data <- speaking.data  %>% filter(str_detect(scale, 
                                                 paste(c("Duration of speaking time"),
                                                    collapse = '|')))

# value sometimes contained text before filtering, we have to convert the numbers to numeric
speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))

speaking.plot <- speaking.data %>%
  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(size = 8)) +
    facet_grid(group~perspective) +
    ggtitle("Boxplot with individual points for Duration of speaking time") +
    xlab("")
speaking.plot

### Eyetracking Data

The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson. The software allows for non-screen based recordings of a participants’ attention while moving in real-world settings. The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video. In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software. Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data. Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form. Tobii Pro does not allow to do AOI based analyses within Pro Lab. So we exported a tsv. file to do further analyses in the software R.

#### Gaze relational index (GRI)

The GRI is a measure of visual expertise in information processing. This metric is calculated as the ratio of mean fixation duration to fixation count. The GRI is higher for novices than for experts. (@gegenfurtner2020gaze)

```{r GRItable, echo = FALSE}

# prepare data (selected from questionnaire data)
et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)

# converting integer to numeric
et.raw.data <- et.raw.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
                                       )

# calculate the GRI 
# create a basic table (tibble) using tidyverse functions
et.raw.table <- et.raw.data %>%
  group_by(Participant, Variable) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "Fixation Duration" = Total_duration_of_whole_fixations,
            "M Duration Fixation" = Average_duration_of_whole_fixations,
            "TOI" = Duration_of_interval,
            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)

# format and insert table in manuscript
apa_table(
  et.raw.table,
  caption = "Number and Duration (in msec) of Fixations",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

################## TEST SECTION

```{r boxplot GRI, fig.width=6, fig.height = 8, echo = FALSE}
# 
# et.plot <- et.raw.data %>%
#   ggplot(aes(x=Number_of_whole_fixations, y=value, fill=scale)) +
#     geom_boxplot() +
#     scale_x_discrete(guide = guide_axis(angle = 70)) +
#     geom_jitter(color="black", size=0.4, alpha=0.9) +
#     theme_light() +
#     theme(
#       legend.position="none",
#       plot.title = element_text(size=11)
#     ) +
#     facet_grid(~Variable)+
#     ggtitle("Boxplot with individual points for Number of fixations") +
#     xlab("")
# et.plot

```{r calibration phase TOI, echo = FALSE}

# prepare data (selected from questionnaire data)
et.calib.data<-read.table("./data/Aperol_pilot_glasses_raw_ALL_metrics_calib_without_AOI_snapshot.tsv", dec=",", sep="\t", header=T)

# converting integer to numeric
et.calib.data <- et.calib.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
                                       )
# select relevant rows 
et.calib.data <- et.calib.data %>% filter(TOI == "Calibration phase")

# calculate the GRI 
# create a basic table (tibble) using tidyverse functions
et.calib.table <- et.calib.data %>%
  group_by(Participant, Variable1) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "Fixation Duration" = Total_duration_of_whole_fixations,
            "M Duration Fixation" = Average_duration_of_whole_fixations,
            "TOI" = Duration_of_interval,
            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)

# format and insert table in manuscript
apa_table(
  et.calib.table,
  caption = "Number and Duration (in msec) of Fixations during calibration",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

#########################################

@@

### Questionnaire Data

### Behavioral Data

### Eyetracking Data

>>>>

affiliation:
  - id            : "1"
    institution   : "University of Leipzig"
  - id            : "2"
    institution   : "MPI for Evolutionary Anthropology, Leipzig"

authornote: |
  The study was carried out with the permission of the Ethics Committee of the University of Leipzig.

@@

documentclass     : "apa6"
classoption       : "man"
output            : word_document #papaja::apa6_pdf
---

@@

@@

## Data collection

@@

For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig. The subjects were divided into groups of four, so the study was conducted on two different sessions. All participants were asked to hold a 10-minute lesson. The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering the questionnaire.

By using mobile eye-trackers, the gaze and behavior of the experts and novices was recorded during the lesson. In addition, the speech and sounds and voices were recorded with an audio recorder installed in the middle of the Lab. Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles. One camera was installed to film the class from the side. Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back. Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.

The lessons recorded on video were coded in a post-hoc procedure with a coding software by previously trained raters. The statistical data have been analyzed by using the program RStudio [Link: https://rstudio.com/].

## Measures

### Questionnaire Data
*Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.*

The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
The scales on the quality of teaching are a validated questionnaire (@helmke2014unterrichtsdiagnostik). Whereas the scales on the teacher's presence behaviour were derived from the research literature (@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen) and were used in the pilot for the first time.

@@

The table below provides an overview over the mean, min, max and standard deviation of all scales.

@@

\newpage
The individual items of a scale were further represented in graphs.

@@

(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention
```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}

@@

```
\newpage
In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE}

@@

```
\newpage
Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment. The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.

```{r Duration speaking time, fig.width=5, fig.height = 5, echo = FALSE}
# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)

# to compare both sessions filter only Identical items
quest.raw.data <- quest.raw.data  %>% filter(str_detect(scale, 
                                                 paste(c("Duration of speaking time"),
                                                    collapse = '|')))
view(quest.raw.data)

speaking.plot <- quest.raw.data %>%
  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(size = 8)) +
    facet_grid(group~perspective) +
    ggtitle("Boxplot with individual points for Duration of speaking time") +
    xlab("")
speaking.plot

### Eye-tracking equipment

A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements. The head unit is a measuring device with different sensitive sensors. A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds. Infrared light illuminators support the eye tracking sensors which record the eye orientation. The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second. The scene camera has a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height). The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.

The Tobii Pro Glasses 2 software allows for non-screen based recordings of a participants’ attention while moving in real-world settings. The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video. In order to map multiple recordings to AOIs, it is necessary to import the eye-tracking recordings into the Tobii Pro Analyzer software. Also, it is necessary to create a reference image of the scene in which one wishes to plot the gaze data (i.e. snapshot). Once the snapshot is imported, the gaze recordings of multiple recordings can be mapped to the reference image and analyzed in aggregated form. Tobii Pro does not allow to do AOI based analyses within Pro Lab. Also, the dependency on snapshot reference images makes this approach impractical when working in different settings, i.e. different classrooms with various participants. Finally, mapping gaze to people or any moving objects complicated the analyses further.

@@
